Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction

### 2019-03-17 Manuscript_draft/Tables_and_figures.Rmd
table of seed production with 100% pollen
edits on table headers

table<- data.frame(Family, Genus, Species)
kable(table, format="markdown", caption = "a")
```
\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%'}
knitr::include_graphics('images/phylo_image.png')
```
**Figure 1**
\newpage
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7}
load("r_biology.RData")
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)
ggplot(bio,aes(x=Species,y=value,fill=variable))+
  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology test")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

@@

>>>>

table<- data.frame(Family, Genus, Species)
kable(table, format="markdown", caption = "a")
```
\newpage

**Table 2**
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("table_treatments.RData")
Species <- c("Brassica oleracea", "Brassica rapa", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
Cross <- cross
Self <- self
Natural_selfing <- nat_self
Apomixis <- apo
table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
kable(table, format="markdown", caption= "Perecentage of seeds produced per ovule for the ten species used in the experiment. The treatments presented are hand cross-pollination, hand self-pollination, natural selfing and apomixis (emasculated flowers).
",longtable = TRUE)
```

**Table 3**
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
dat_all <- readRDS("Data/dat_all.RData")
kable(dat_all, format="markdown", caption = "a")

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%'}
knitr::include_graphics('images/phylo_image.png')
```
**Figure 1**
\newpage
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7}
load("r_biology.RData")
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)
ggplot(bio,aes(x=Species,y=value,fill=variable))+
  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology test")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

@@

**Table 2** Results of hand corss-pollination, hand self-pollination, natural selfing (unpollinated bagged flowers) and apomixis. The values are the average seed production per treatment (N=10) divided by the average number of ovules per species.

**Table 3** Seed production for the treatments that produced seeds with 100% foeign pollen.
